Proportional multi-state multiple-cohort life table model

### 2018-04-23 MSLT/MSLTdoc.Rmd
Data inputs dismod
Incomplete

@@

for(sex_index in i_sex) {
  for (measure_index in i_measure) {
    for (disease_index in i_disease) {

data <- filter(GBDGL, measure == measure_index, sex == sex_index, 
cause == disease_index) %>% select(measure, location, sex, age, metric, 
cause, val, age_cat, one_rate, sex_age_cat) 
colnames(data)[9] <- paste(measure_index, disease_index, sep =  "_")
assign(paste(sex_index, measure_index, disease_index, sep = "_"), data)
## Give one rate a name to match merge in data_dismodii input
    }
  }
}

@@

 for (measure_index in i_measure) {
    for (disease_index in i_disease) {

  # data_dismodii[,paste(measure_index, disease_index, sep =  "_")] <- 0
data_dismodii  <- merge(data_dismodii, select(female_deaths_interpolated
                                                     ,c(sex_age_cat, mx))
                                                     , by = 'sex_age_cat', all.x = TRUE)
  }
 }

for (measure_index in i_measure) {
    for (disease_index in i_disease) {
      for (sex_index in i_sex){

data_dismodii  <- merge(data_dismodii, select(paste(sex_index, measure_index, disease_index, sep = "_"),c(sex_age_cat, paste(measure_index, disease_index, sep = "_")), by = 'sex_age_cat', all.x = TRUE))

    }
  }
}

# data_dismodii  <- merge(data_dismodii, select(male_deaths_interpolated
#                                                      ,c(sex_age_cat, mx))
#                                                      , by = 'sex_age_cat', all.x = TRUE)

>>>>

####THIS CODE IS INCOMPLETE, I WILL PREPARE THE DATA FOR DISMOD II IN EXCEL AND AFTER PRESENTATION THURSDAY 26 APRIL I WILL DEVELOP THE SCRIPT.

@@

## Loop to generate dataframes
for(sex_index in i_sex) {
  for (measure_index in i_measure) {
    for (disease_index in i_disease) {

data <- filter(GBDGL, measure == measure_index, sex == sex_index, 
cause == disease_index) %>% select(measure, location, sex, age, metric, 
cause, val, age_cat, one_rate, sex_age_cat) 
colnames(data)[9] <- paste(measure_index, disease_index, sep =  "_")
assign(paste(sex_index, measure_index, disease_index, sep = "_"), data)

## The code below is not generating the multiple datasets saved as csv.

# data_name <- file.path(tempdir(), paste0(sex_index, measure_index, disease_index, ".csv"))
# write.csv(data, file = data_name)
    }
  }
}

## Generate TO DO, ADD disease parameters.

@@

#  for (measure_index in i_measure) {
#     for (disease_index in i_disease) {
# 
#   # data_dismodii[,paste(measure_index, disease_index, sep =  "_")] <- 0
# data_dismodii  <- merge(data_dismodii, select(female_deaths_interpolated
#                                                      ,c(sex_age_cat, mx))
#                                                      , by = 'sex_age_cat', all.x = TRUE)
#   }
#  }
